Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-11-09 manuscript.tex
Fix compiliation of paper

The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
        \toprule
        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
        \midrule
        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
        \bottomrule
    \end{tabular} 
    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
\end{table}
The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
\Gls{lidar} measurements are generated until the total uncertainty
\begin{align*}
    \sum_i w_i,
\end{align*}
is sufficiently small.
In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/geographos/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_1872.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_3745.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_5617.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_7489.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/truth.jpg}}
    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_1321.jpg}}\\%

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_2643.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_3964.jpg}}\\%

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_5285.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/truth.jpg}}
    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
\end{figure}
\paragraph{Asteroid 52760 Reconstruction}

>>>>

The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
        \toprule
        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
        \midrule
        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
        \bottomrule
    \end{tabular} 
    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
\end{table}
The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
LIDAR measurements are generated until the total uncertainty
\begin{align*}
    \sum_i w_i,
\end{align*}
is sufficiently small.
In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented here. 
% TODO Add polyhedron volume algorithm

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/geographos/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_1872.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_3745.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_5617.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_7489.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/truth.jpg}}
    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
\end{figure}
\paragraph{Asteroid 52760 Reconstruction}
